---
output: github_document
---

# rapporteuR

<!-- badges: start -->
[![R build status](https://github.com/ElliottMess/rapporteuR/workflows/R-CMD-check/badge.svg)](https://github.com/elliottMess/rapporteuR/actions)
<!-- badges: end -->

The goal of rapporteuR is to facilitate reporting on the World Health Organization’s Triple Billions framework.

## Installation

You can install rapporteuR from [GitHub](https://github.com/) with:

```{r install, eval=FALSE, include=FALSE}
# install.packages("devtools")
devtools::install_github("ElliottMess/rapporteuR")
```

## Demonstration dataset

A demonstration dataset is provided in the dataset. It does not reflect actual data for the countries included. It serves only to demonstrate the functions of the package.

```{r}
library(rapporteuR)

head(all_billions_example)

```

## Country Summary Sheets

Country summary sheets are country-specific Excel files reporting on the Triple Billions.

Two functions exists:
* `export_country_summary_xls()` : export a specific country
* `export_all_countries_summaries_xls()` : export all countries present in the dataset

The `billion` parameter allows to export a specific billion or all at once.

```{r example-all_billions, eval=FALSE}
# Export HEP summary for Afghanistan:
export_country_summary_xls(all_billions_example, "AFG", "hep")

# Export all billions for Canada:
export_country_summary_xls(all_billions_example, "CAN", "all")

# By default, files are saved to "outputs" folder, but this can be modified with `output_folder'.
# If the folder doesn't exists, it will be created (recursively).
export_country_summary_xls(all_billions_example, "CAN", "all", output_folder = "outputs/all/CAN")

# Exporting all billions for all countries in the dataset:
export_all_countries_summaries_xls(all_billions_example, "all", output_folder = "outputs/all")

```
