---
title: "Country summary Excel files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Country summary Excel files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

---
title: "Country summary Excel files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Country summary Excel files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Country summary sheets are country-specific Excel files reporting on the Triple Billions.

Two functions exists:
* `export_country_summary_xls()` : export a specific country
* `export_all_countries_summaries_xls()` : export all countries present in the dataset

The `billion` parameter allows to export a specific billion or all at once.

```{r example-all_billions, eval=FALSE}
library(rapporteur)

# Export HEP summary for Afghanistan:
export_country_summary_xls(all_billions_example, "AFG", "hep")

# Export all billions for Canada:
export_country_summary_xls(all_billions_example, "CAN", "all")

# By default, files are saved to "outputs" folder, but this can be modified with `output_folder'.
# If the folder doesn't exists, it will be created (recursively).
export_country_summary_xls(all_billions_example, "CAN", "all", output_folder = "outputs/all/CAN")

# Exporting all billions for all countries in the dataset:
export_all_countries_summaries_xls(all_billions_example, "all", output_folder = "outputs/all")

```
