---
title: "Indicator time series plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Indicator time series plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rapporteur)
library(billionaiRe)
```

The indicator time series plots allow to plot Triple Billion time series. They take into consideration the structure of `scenario` (see the `Scenarios` vignette in billionaiRe) and output appropriate plots to PDF.

The functions are split into first generating ggplot objects, and set exporting and binding to PDF, which can allow internal users to re-use the functions to export to other formats.

```{r example, eval=FALSE}
test_data <- load_misc_data("test_data/test_data/test_data.parquet") %>%
  dplyr::mutate(value = dplyr::case_when(
    scenario == "covid_dip_lag" & year <= 2020 ~ NA_real_,
    scenario == "covid_dip_lag" ~  dplyr::if_else(.data[["value"]] - 10.0 >0, .data[["value"]] - 10.0, 0),
    TRUE ~ .data[["value"]]
  )) %>%
  dplyr::filter(!is.na(value))

temp_dir <- tempdir()

export_plot_timeseries_indicator_pdf(test_data,
                                     indicator = "anc4",
                                     output_folder = temp_dir)


```
